---
title: "projectPackage-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{G11_package-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE, echo = FALSE, error = FALSE}
library(projectPackage)

```

## Introduction to projectPackage

The goal of projectPackage is to provide simplified functions to achieve the goal of data preprocessing for exploratory data analyses. The projectPackage makes the following steps quick and easy:

-   Removing certain columns from a data set
-   Creating a ggpairs correlation plot
-   Creating a recipe for knn model

This document introduces you all of the tools mentioned above as well as examples of how to apply them to data frames and use them in different real-world scenarios.

## Data: mtcars

For the purpose of demonstration, we will use a basic data set called mtcars. This data set has 11 columns, 32 rows and is documented in ?mtcars. Note that "mtcars" is a data frame and below is the first 6 rows.

```{r dataset, warning=FALSE, echo = FALSE}
head(mtcars)
data <- mtcars
```

## Demonstration of basic functions in projectPackage

## 1. Dropping columns with data_cleaning()

Often when you work with large data sets, there will be columns that are redundant or not of interest. In that case, you can use our function data_cleaning() to drop those columns. For details on how to use the function, check out help(data_cleaning).

-   **dropping a single column "mpg" from mtcars**

```{r data_cleaning1, warning = FALSE, error = FALSE}
head(data_cleaning(data, "mpg"))
```

As you can see above, the column mpg has been dropped from the data frame.

-   **dropping multiple columns from mtcars**

```{r data_cleaning2, warning = FALSE, error = FALSE}
head(data_cleaning(data, c("mpg","disp","qsec")))
```

Again, columns mpg, disp and qsec has been dropped.

-   **When an inappropriate column name is inputted, an error will occur.**

For instance, if I accidentally used the wrong column name mpf instead of mpg. The function will kindly produce an error.

data_cleaning(data, "mpf") will produce the following message: *"Error in data_cleaning(data, "mpf") : column name does not exist in the data frame"*

## 2. Creating a ggpairs correlation plot

## 3. Creating a recipe for knn model
